Election Violence Newspaper Article Selection Process Pilot: Evaluate Keyword Selection Method

### 2018-08-09 other_R_code/article_selection_pilot_evaluate_keywordmethod.Rnw
implementation pilot functions

\section{Assess Naive Bayes selection performance on 4 keywords (binary dfm)}
\label{sect:eval4nb}
Here there are four keywords (election, riot, disturbance, incident) which are either present (1) or not-present (0). Use these patterns to identify election violence articles with a Naive Bayes classifer.
<<subset.on.keywords.eval.four.words>>=

@@

>>>>

\section{Download Initial 1832 Cases}
\label{sect:download1832}
We run three searches on the BNA. election riot, election incident, election disturbance. The code below returns these search results (including the description text) as stored on the database.

A (slightly adjusted) version of the url is used to detect and remove material which is in the classified set above.

I also add indicators that this material is not classified (\texttt{classified==0}) and that it is unclassified (\texttt{unclass==1}) which will be useful when added to the classified material above.

(Note: infact these searches have been run multiple times in 1832 probably for experimentation reasons - presumably because they were run very close in time to each other with no new material added the results are identical - for this reason I have just chosen one instance of each of the three searches).
<<initial.1832.results>>=

\section{Use classifier to decide which documents to download full ocr}
\label{sect:whichdownloadocr}

<<subset.on.description>>=

\section{Use classifier to decide which of the downloaded documents to code}
\label{sect:whichcode}

<<subset.on.ocr>>=

@
\section{Use classifier on keywords only to decide which documents to download}
<<subset.on.keywords>>=

\section{Then use classifier on ocr}
\label{sect:useonocr}
<<subset.on.ocr.after.keyword>>=

Using keywords only we find:
That of \Sexpr{nrow(unclass_i_1832)} articles returned by search:
\begin{itemize}
  \item \Sexpr{nrow(code_these_fromkeywords_ocr)} are designated for coding
  \item \Sexpr{nrow(do_not_code_these_fromkeywords)} are not coded
  \item \Sexpr{nrow(download_these_fromkeywords)} are identified for download
  \item \Sexpr{nrow(unclass_i_1832)-nrow(download_these_fromkeywords)} are rejected without downloading

\end{itemize}
\section{Assess Naive Bayes selection performance on 4 keywords (binary dfm)}
\label{sect:eval4nb}
Here there are four keywords (election, riot, disturbance, incident) which are either present (1) or not-present (0). Use these patterns to identify election violence articles with a Naive Bayes classifer.
<<subset.on.keywords.eval.four.words>>=

@@

@
\section{Some Case: These Cases have been rejected for coding using Naive Bayes (second stage on keyword classification only)}
\label{sect:rejectnbprocess}
<<print.random.not.code.fromkeywords.cases, results='asis'>>=
